\sysfull

### 2018-04-17 paper/evaluation.tex

\begin{wrapfigure}{t!}{0.5\textwidth}
	%\begin{figure}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/coalEfficiency}
    \caption{Breakdown of overhead for the proposed coalescing strategies
relative to the baseline without coalescing.
NC: no coalescing, EB: energy-blind coalescing, EA: energy-aware coalescing, ETA:
energy- and task-aware coalescing. All coalescing strategies reduce total
overhead and maximize useful work. EA and ETA perform better than EB.
\todo{rename legend entry 'user code' with 'useful task code'; rename y-axis to
'Time usage (\%)'; increase font by
two more points everywhere}{Amjad}}
	\label{fig:overallOverheadBreakdown}
	%\end{figure}
\end{wrapfigure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.49\columnwidth]{figures/overallOverhead}
	\includegraphics[width=0.49\columnwidth]{figures/memAccess}
	\caption{\sys kernel overhead: a breakdown of time spent in
the application and in the runtime (left) and a breakdown of protected memory
accesses into three types with different costs. NC: no coalescing, EA:
energy-aware coalescing, ETA: energy- and task-aware coalescing. \todo{rename
legend entry 'task code' to 'user code'; rename y-axis to 'Load (\%)'}{Amjad}}
	\label{fig:coalEfficiency}
\end{figure}

>>>>

\begin{wrapfigure}{t!}{0.5\textwidth}
	%\begin{figure}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/coalEfficiency}
    \caption{Breakdown of overhead for the proposed coalescing strategies
relative to the baseline without coalescing.
NC: no coalescing, EB: energy-blind coalescing, EA: energy-aware coalescing, ETA:
energy- and task-aware coalescing. All coalescing strategies reduce total
overhead and maximize useful work. EA and ETA perform better than EB.}
	\label{fig:overallOverheadBreakdown}
	%\end{figure}
\end{wrapfigure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.49\columnwidth]{figures/overallOverhead}
	\includegraphics[width=0.49\columnwidth]{figures/memAccess}
	\caption{\sys kernel overhead: a breakdown of time spent in
the application and in the runtime (left) and a breakdown of protected memory
accesses into three types with different costs. NC: no coalescing, EA:
energy-aware coalescing, ETA: energy- and task-aware coalescing.}
	\label{fig:coalEfficiency}
\end{figure}
